\chapter{Abstract}
Nowadays, working environments do not present workers with a continous stream of recurring tasks like at the assembly line. Instead, highly skilled employees with diverse competencies work in dynamic teams to complete nonrepeating projects.
As a consequence, project driven organizations face the problem of constantly needing to put teams together based on the members’ skills, experience, motivation and personal preferences. At SinnerSchrader, like in many businesses, there is no central source of information about this data.
This thesis covers the design and partial implementation of a web application custom-tailored to SinnerSchrader that provides a simple way to manage employees' skills and interests. The person search function - its central feature - uses a novel approach of rating employees based on not only on their skills but also their interests in order to find the most suitable employee for the user's search query.
The requirements for such an application have been compiled by conducting semi-structured interviews with representatives of the main groups of stakeholders.
The legal framework has been analyzed to detect possible concerns including the Works Council's objection against the possibility of mutual ratings.
The concept behind the application including said search functions and recommender systems to enrich the user experience has been constructed and implemented using state of the art web technologies. To validate that the application, and especially the novel scoring approach, is capable of fulfilling the users’ needs, a survey has been conducted and interpreted. The backend implemenatation has been tested regarding both functional and non-functional requirements.
