\chapter{SinnerSchrader}

The SinnerSchrader Group is a full service web agency based in Hamburg aggregating the subcompanies SinnerSchrader Deutschland, SinnerSchrader Content, SinnerSchrader Commerce and SinnerSchrader Swipe. The broad spectrum of expertise,including, but not limited to, digital communication strategies, visual and interaction design,  technical architecture, full stack development, editorial services, content production, E-Commerce, mobile app development, hosting, and maintenance, allows SinnerSchrader to serve all needs regarding their customer’s digital transformation. The combination of all said competencies under one single roof reduces organisational friction between the discipline-specific teams because they all share the same vision of the big picture they are creating. This does not only lead to faster development cycles, but also to a more coherent and unified product.

\subsection{Project-Driven Business}
As a web agency, it is clear that SinnerSchrader has to operate in a project-driven way. This means there no continuous stream of recurring work repeating constantly, but many different projects for different clients, each one dealing with varying challenges and questions. From a technical point of view, the diversity of know-how needed for each project is extremely huge since every application uses its own dedicated stack of technologies. As a consequence, the developers’ skill sets are based on the combination of projects they have worked on and their general field of interest. This results in one problem: Managers frequently have to put teams together based on the members’ skills with respect to the individual requirements of the project.\newline
This thesis will cover the creation of a tool helping managers with that problem by providing a centralized source of data about each employee’s professional abilities.

\subsection{Matrix Organisation}
TODO
team manager
supervisor
hübsches Bild
